Conjure: Summoning Proxies from Unused Address Space

### 2019-09-20 paper/paper.tex
Update ACM format, add authors and acknowledgements

\documentclass[sigconf,anonymous]{acmart}
%\usepackage{usenix2019_v3}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%% \setcopyright{acmcopyright}
%% \copyrightyear{2019}
%% \acmYear{2019}
%% \acmDOI{10.1145/1122445.1122456}

%% %% These commands are for a PROCEEDINGS abstract or paper.
%% \acmConference[CCS '19]{CCS '19: ACM Conference on Computer and Communications
%% Security}{November 11--15, 2019}{London, UK}
%% \acmBooktitle{CCS '19: ACM Symposium on Computer and Communications Security,
%%   November 11--15, 2019, London, UK}
%% \acmPrice{0.00}
%% \acmISBN{978-1-4503-9999-9/18/06}

\fancyhf{} % Remove fancy page headers                                                                
\fancyhead[C]{Anonymous submission \#610 to ACM CCS 2019}
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions                                     
\acmConference[Anonymous Submission to ACM CCS 2019]{ACM Conference on Computer and Communications Security}{Due 15 May 2019}{London, TBD}
\acmYear{2019}

\settopmatter{printacmref=false, printccs=true, printfolios=true}

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
%\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
%\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{microtype}
\SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
\usepackage[font=small]{caption}
\microtypecontext{spacing=nonfrench}
%\usepackage{subcaption}
\usepackage{paralist}
\usepackage{xspace}
\usepackage{soul}
\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
\newcommand{\nikita}[1]{\note{nikita}{#1}}
\newcommand{\TODO}[1]{\hl{TODO: #1}\xspace}
\newcommand{\TK}{\hl{TK}\xspace}

% Slight JAH fix to stop URLs from breaking after ``http:''
\def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]%
 \do\)\do\,\do\?\do\'\do+\do\=\do\#}
\def\UrlBigBreaks{\do\:\do\/}%
\urlstyle{rm}

\widowpenalty=10000
\clubpenalty=10000

@@

@@

\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
%\title{\Large \bf Dark Decoys:
%  Conjuring Proxies from Unused Address Space}
\title{Conjure: Summoning Proxies from Unused Address Space}

%\author{Anonymized for review}
%for single author (just remove % characters)
%\author{
%{\rm Your N.\ Here}\\
%Your Institution
%\and
%{\rm Second Name}\\
%Second Institution
%% copy the following lines to add more authors
%% \and
%% {\rm Name}\\
%%Name Institution
%} % end author

%\newcommand{\scheme}{Dark Decoys\xspace}
\newcommand{\scheme}{Conjure\xspace}

@@

@@

\bibliographystyle{plain}
\small
\bibliography{biblio}

\appendix

\input{rebuttal}

>>>>

\documentclass[sigconf]{acmart}

\settopmatter{printacmref=true}

\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{dblfloatfix} % magic
\usepackage{balance}
\usepackage{paralist}
\usepackage{wasysym}
\usepackage{xparse}
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\urlstyle{rm}

% From CCS template:
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Fix URL hyphenation (AH 12/2008)
\def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]%
 \do\)\do\,\do\?\do\'\do+\do\=\do\#}
\def\UrlBigBreaks{\do\:\do\/}%

\newcommand{\todo}[1]{}
\renewcommand{\todo}[1]{{\color{red} TODO: {#1}}}
\newcommand{\TODO}[1]{}
\renewcommand{\TODO}[1]{{\color{red} TODO: {#1}}}
\newcommand{\TK}{}
\renewcommand{\TK}{{\color{red}TK}\xspace}

@@

\copyrightyear{2019}
\acmYear{2019}
\acmConference[CCS '19]{2019 ACM SIGSAC Conference on Computer and Communications Security}{November 11--15, 2019}{London, United Kingdom}
\acmBooktitle{2019 ACM SIGSAC Conference on Computer and Communications Security (CCS '19), November 11--15, 2019, London, United Kingdom}
\acmPrice{15.00}
\acmDOI{10.1145/3319535.3363218}
\acmISBN{978-1-4503-6747-9/19/11}
\setcopyright{rightsretained}

\include{figures}

@@

\fancyhead{} % From CCS template.

\title{Conjure: Summoning Proxies from Unused Address Space}

\author{Sergey Frolov}\affiliation{University of Colorado Boulder}
\author{Jack Wampler}\affiliation{University of Colorado Boulder}
\author{Sze Chuen Tan}\affiliation{UIUC}
\author{J. Alex Halderman}\affiliation{University of Michigan}
\author{Nikita Borisov}\affiliation{UIUC}
\author{Eric Wustrow}\affiliation{University of Colorado Boulder}

\newcommand{\scheme}{Conjure\xspace}

@@

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10003033.10003083.10003014</concept_id>
  <concept_desc>Networks~Network security</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10003456.10003462.10003480</concept_id>
  <concept_desc>Social and professional topics~Censorship</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[300]{Networks~Network security}
\ccsdesc[300]{Social and professional topics~Censorship}

@@

\begin{acks}
  The authors thank the incredible partner organizations that have
  made deployment of Refraction Networking a reality, especially Merit
  Network and Psiphon. We also thank \TODO{anyone else?} the
  University of Colorado IT Security and Network Operations
  staff. This material is based in part upon work supported by the
  U.S. National Science Foundation under Awards \TODO{others?}
  CNS-1518888 and OAC-1925476.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\balance
\bibliography{biblio}

%\appendix
%\input{rebuttal}
